---
title: "R Notebook"
output: html_notebook
---


```{r}
install.packages(c("MALDIquant", "MALDIquantForeign"))
```

```{r}
library(MALDIquant)
library(MALDIquantForeign)

```
```{r}
s <- createMassSpectrum(mass= 1:10, intensity= 1:10 
                        + metaData=list(name="Spectrum1"))
```
```{r}
data(fiedler2009subset)
```
```{r}
length(fiedler2009subset)

fiedler2009subset [1:2]
```
```{r}
R1 <- fiedler2009subset
```
Testing Same amount of DATA points
```{r}
any(sapply(R1,isEmpty))
```
```{r}

table(sapply(R1,length))
```
```{r}
plot(R1[[1]])
```

```{r}
spectra <- transformIntensity(R1,method= "sqrt")
spectra <- smoothIntensity(spectra, method = "SavitzkyGolay", halfWindowSize = 10)
baseline <- estimateBaseline(spectra[[16]],method="SNIP", iterations = 100)
```
Visualization of the Variance Staqbilization, SMoothing, Baseline Correction. Use this to determine if baseline is good.
```{r}
plot(spectra[[16]])
lines(baseline, col="red", lwd = 2)
```
```{r}
spectra <- removeBaseline(spectra, method = "SNIP", iterations = 100)
plot(spectra[[1]])
```
NMomrlaization of the intenisty values
```{r}
spectra <- calibrateIntensity(spectra, method = "TIC")
```
```{r}
spectra <- alignSpectra(spectra, halfWindowSize=20, SNR=2,tolerance=0.002, warpingMethod="lowess")
```
```{r}
samples <- factor(sapply(spectra, function(x)metaData(x)$sampleName))
```
```{r}
avgSpectra <- averageMassSpectra(spectra, labels=samples, method="mean")
```
```{r}
noise <- estimateNoise(avgSpectra[[1]])
plot(avgSpectra[[1]], xlim=c(4000, 5000), ylim=c(0, 0.002))
lines(noise, col="red")
lines(noise[,1], noise[,2]*5, col="blue")
```

```{r}
peaks <- detectPeaks(avgSpectra, method="MAD",
halfWindowSize=20, SNR=6)
plot(avgSpectra[[1]], xlim=c(4000, 5000), ylim=c(0, 0.002))
points(peaks[[1]], col="red", pch=4)
```

```{r}
peaks <- binPeaks(peaks, tolerance=0.002)
```

```{r}
peaks <- filterPeaks(peaks, minFrequency=0.25)
```
```{r}
featureMatrix <- intensityMatrix(peaks, avgSpectra)
head(featureMatrix[, 1:3])
```

OK NOLANDO: You have sucessfully imported DATA here is what yyou did.

```{r}
setwd("~/R/MaldiNB2/RawData")
MDD<-setwd("~/R/MaldiNB2/RawData")
MDI <- importMzXml(MDD)
```
Recongonize you set the WD by doing it the small window on the right with  the paths just click on the more button and hit setwd. Set that to a variable and then you can import using maldiquantforiegn.
```{r}
View(MDI)
length(MDI)
```
```{r}
any(sapply(MDI,isEmpty))
table(sapply(MDI,length))
```
```{r}
plot(MDI[[1]])
```

```{r}
spectraMDI <- transformIntensity(MDI,method= "sqrt")
spectraMDI <- smoothIntensity(spectraMDI, method = "SavitzkyGolay", halfWindowSize = 10)
baselineMDI <- estimateBaseline(spectraMDI[[1]],method="SNIP", iterations = 100)
```
```{r}
plot(spectraMDI[[1]])
lines(baselineMDI, col="red", lwd = 2)
```

```{r}
spectraMDI <- removeBaseline(spectraMDI, method = "SNIP", iterations = 100)
plot(spectraMDI[[1]])
```
```{r}
spectraMDI <- calibrateIntensity(spectraMDI, method = "TIC")
spectraMDI <- alignSpectra(spectraMDI,SNR=2,tolerance=0.002, warpingMethod="lowess") 
#This is not workinb bc Referece MassPeaks object contains no peaks. Not sure if it is suggesting i have no peaks in my spectra . Maybe?
samplesMDI <- factor(sapply(spectraMDI, function(x)metaData(x)$sampleName))
avgSpectraMDI <- averageMassSpectra(spectraMDI, method="mean")
```
```{r}
plot(spectraMDI[[1]])
```
```{r}
noiseMDI <- estimateNoise(spectraMDI[[1]])
plot(spectraMDI[[1]], xlim=c(50, 300), ylim=c(0, 0.1))
lines(noiseMDI, col="red")
lines(noiseMDI[,1], noiseMDI[,2]*3, col="blue")
```


OOK I UNDERSTAND WHAT I AM DOING NOW. SO LISTEN YOU NEED TO SCALE TO THE GRAPH. IF YOU DONT THEN NOTHING MAKES SENSE CAUSE NOTHING IN THE SCALE> LOOK AT THE X And Y axis and set accoding.

```{r}
peaksMDI <- detectPeaks(spectraMDI, method="MAD",
halfWindowSize=20, SNR=3)
plot(spectraMDI[[1]], xlim=c(50,300), ylim=c(0, 0.10))
points(peaksMDI[[1]], col="red", pch=4)
```
